Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-04-12 Paper/paper.tex
update errorbar vs N figure

\includegraphics[width=.9\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L2000.pdf}
\includegraphics[width=.9\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L1500.pdf}\\
\includegraphics[width=.67\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L1000.pdf}
\includegraphics[width=.67\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L800.pdf}
\includegraphics[width=.67\columnwidth]{plots/FillBetweenNormErrorBarsLambda_vs_N_L500.pdf}

@@

>>>>

\includegraphics[width=.9\columnwidth]{plots/FillBetweenErrorBarsLambda_vs_N_L2000.pdf}
\includegraphics[width=.9\columnwidth]{plots/FillBetweenErrorBarsLambda_vs_N_L1500.pdf}\\
\includegraphics[width=.67\columnwidth]{plots/FillBetweenErrorBarsLambda_vs_N_L1000.pdf}
\includegraphics[width=.67\columnwidth]{plots/FillBetweenErrorBarsLambda_vs_N_L800.pdf}
\includegraphics[width=.67\columnwidth]{plots/FillBetweenErrorBarsLambda_vs_N_L500.pdf}

@@

The pioneering terrestrial observation of gravitational waves by Advanced LIGO
harbingers the dawn of an era of gravitational-wave astronomy where 
observations, more than theory, would play the driving role. Binaries of 
compact stellar objects evolve under the radiation reaction force of emitting
gravitational waves.
